On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 hamiltonian.tex
Fix LaTeX warnings
Wrap up blindness first draft
Make another algorithm env change

\section{The History XZ Local Hamiltonian}

@@

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
		%The $X$ and $Z$ measurement results of $C(x)$ and the first $n$ qubits of $C'(x||0)$ are identically distributed.
	\end{itemize}
\end{theorem}

@@

\subsection{Reducing $\SampBQP$ to  local Hamiltonian }

@@

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
	\begin{algorithmic}[1]
		\Require $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$
		\Procedure{GroundStateCheck}{$\ket\phi$}
		\State Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State Set $p_S = \frac{|d_S|}{D}$
		\State Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
		\State  Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
		\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
		\State Accept
		\Else
		\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

>>>>

\section{The History XZ Local Hamiltonian}
\label{sec:Hamiltonian}

@@

\begin{theorem}
	Let $C$ be a circuit that:
	\begin{itemize}
		\item consists of either $H$ or $\Lambda(P(i))$, and the number of gates is $T$.\hannote{confusing?}
		\item uses $n$ qubits
	\end{itemize}
	Then a classical machine given $C$ can compute a circuit $C'$ that:
	\begin{itemize}
		\item consists of at most $4T$ gates, each either $H$ or $\Lambda^2(X)$ \hannote{don't like this notation}.
		\item uses $n+1$ qubits
		\item Let $x\in\set{0,1}^n$. Let $x|| 0\in\set{0,1}^{n+1}$ be $x$ concatenated with $0$.
		The measurement result of a tensor product of $X$ and $Z$ operators on the first $n$ qubits of $C'(x||0)$ has the same distribution as that on $C(x)$.
	\end{itemize}
\end{theorem}

@@

\subsection{Reducing quantum circuit to  local Hamiltonian }

@@

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
		Let $\ket\phi$ be the potential ground state to check
		\begin{itemize}
			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\item Set $p_S = \frac{|d_S|}{D}$
			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
		\end{itemize}
\end{algorithm}
